---
title: "Data 612 Project"
author: "Collin Coil, Nick Chen"
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: "hide"
    number_sections: TRUE
    toc: true
    toc_float: true
    code_download: true
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = 'C:/Users/colli/OneDrive/Documents/Programming-in-R-Project/')
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = TRUE)
```

```{r package-setup}
library(tidyverse)
library(spgwr)
library(ggmap)
library(maps)
library(mapdata)
library(knitr)
```


# Data used in the study
```{r data-upload-and-glimpse}
BnB_data <- read_csv("Project_Data/BnB_data.csv")
BnB_data2 <- data.frame(BnB_data)
kable(head(BnB_data)[,1:8])
```
The data used in the project comes from a research study by Kristof Gyodi and 
Lukasz Nawaro. The data can be accessed using [this link](https://raw.githubusercontent.com/CollinCoil/Programming-in-R-Project/main/Project_Data/BnB_data.csv). Above, 
you can see the first few columns and rows of this tibble. Additional code has 
been provided to change the tibble into a data frame, but that data frame is not 
used further in this work. The data frame in this study has `r dim(BnB_data)[1]` 
rows and `r dim(BnB_data)[2]` columns. The variables included in this include 
realSum, the price of accommodation for two people and two nights in Euros; 
room_type, the type of accommodation; person_capacity, the maximum number of 
guests; cleanliness_rating, a measure of the cleanliness; dist, the distance 
from the city center in kilometers; metro_dist, the distance to the nearest 
metro station in kilometers; and other variables. This data frame also includes 
information about the latitude and longitude of each Airbnb listing. 

<br>
<br>

# Exploratory Data Analysis

We are trying to understand the determinants of Airbnb prices in ten European 
cities. First, we conducted some simple data analysis. 

```{r simple-data-analysis-1}
BnB_data %>%
  count(City) %>%
  arrange(desc(n))
```

As we see in the table above, there are ten cities in the study, and most of 
the Airbnb observations were in London and Rome. 


```{r simple-analysis-2}
BnB_data %>% 
  group_by(City) %>% 
  summarize(mean_rate = mean(realSum))
```

The table above shows the average two-night price in Euros for an Airbnb in 
each city in the study. However, this can be further broken down because our 
data set has observations for both weekends and weekdays. 

```{r simple-analytics-3}
BnB_data %>%
  group_by(City, Time) %>%
  summarize(price = mean(realSum)) 
```

As we can see, an Airbnb generally costs more on average during the weekends. 
This can also be seen in a graph of the data. 

```{r simple-graph-1}
BnB_data_summarized <- BnB_data %>%
  group_by(City, Time) %>%
  summarize(price = mean(realSum)) %>%
  arrange(desc(price))

ggplot(data = BnB_data_summarized) +
  geom_bar(mapping = aes(x = reorder(City, price), y = price, fill = Time), stat = "identity", position=position_dodge()) +
  geom_text(aes(x = City, y = price, label = round(price), group = Time), 
            position = position_dodge(width = .9), vjust = -.5, size = 3, color ="black")+
  labs(title = "Mean price of Airbnb listings in European Cities", y = "Mean Price (Euros)", 
       x = "City") +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) + 
  theme_bw()
```

Since one of the main goals of this project is to understand how proximity to 
the city center impacts Airbnb listing price, here is a scatter plot of price
vs distance. 

```{r simple-graph-2}
ggplot(data = BnB_data, mapping = aes(x = log(dist), y = log(realSum))) + 
  geom_point() + 
  theme_bw() + 
  labs(title = "Airbnb price vs Distance to City Center", y = "Log Price (Euros)", x = "Log Distance (km)") + 
  geom_smooth(formula = y~x, method = lm, se = FALSE, color = "firebrick")
```

As we can see, there appears to be a negative relationship between Airbnb price 
and distance to the center of a city, but we need to test this relationship. 

<br>
<br>


# Map Making

To better understand the spatial distribution of our Airbnb units and their prices, 
we made several maps. 

```{r map-making-loop}
city_names <- c("Amsterdam", "Athens", "Barcelona", "Berlin", "Budapest", "Lisbon", "London", "Paris", "Rome", "Vienna")

map_data <- paste("Maps/", city_names, "Map.RData", sep = "")

for (data in map_data){
  load(print(data))
}


for (name in city_names) {
  filtered <- BnB_data %>%
    filter(City == name)
  gradient_max <- quantile(filtered$realSum, prob = .75) + 1.5*(quantile(filtered$realSum, prob = .75) - quantile(filtered$realSum, prob = .25))
  max_lng <- max(filtered$lng)
  min_lng <- min(filtered$lng)
  max_lat <- max(filtered$lat)
  min_lat <- min(filtered$lat)
  map_lng <- (max_lng + min_lng)/2
  map_lat <- (max_lat + min_lat)/2
  
  city_map <- get(paste(tolower(name), "Map", sep = ""))
  
  map<- ggmap(city_map) + 
    geom_point(data = filter(BnB_data, City == name),
               mapping = aes(x=lng,y=lat, color = realSum), size = .9) +
    scale_colour_gradientn(
      colours=c('red','yellow','green'), 
      limits=c(0,gradient_max), 
      oob = scales::squish) +
    scale_x_continuous(limits = c(min_lng, max_lng), expand = c(0, 0)) +
    scale_y_continuous(limits = c(min_lat, max_lat), expand = c(0, 0)) +
    labs(title = paste("Mapping of AirBnB Listings in", name), y = "Latitude", 
         x = "Longitude", color = "Price") 
  map_name <- paste(name, "MapPrint", sep = "_")
  assign(map_name, map)
}



Amsterdam_MapPrint

Athens_MapPrint

Budapest_MapPrint

Barcelona_MapPrint

Lisbon_MapPrint

London_MapPrint

Paris_MapPrint

Rome_MapPrint

Vienna_MapPrint
```



Now we need to rigorously test the association between price and distance to 
the city center. 

<br>
<br>
<br>

# Geospatial Regression 

We ran a geospatial regression using the `spgwr` package. This allows us to 
account for spatial autocorrelation in our data. First, we need to mutate our 
data set to match the requirements for `spgwr::gwr`. All variables that are 
used in the regression need to be numeric, so the following code changes the 
tibble to align with the requirements. 

```{r data-reformatting}
BnB_data <- BnB_data %>% mutate(across(where(is.character), as.factor)) %>% 
  mutate(across(where(is.logical), as.factor)) %>% 
  select(!room_type)

BnB_data <- fastDummies::dummy_cols(BnB_data, 
                                    select_columns = c("room_shared", "room_private", "host_is_superhost", "Time", "City"),
                                    remove_selected_columns = TRUE)


coordinates <- data.matrix(BnB_data[,14:15])
```



Do not run the following code. It takes hours to run. Please refer to the 
bandwidth value I calculated from running this once. 

```{r bandwidth-selection, eval=FALSE}
gwr.sel(formula = log(realSum) ~ room_shared_TRUE + person_capacity + 
                              host_is_superhost_TRUE + multi + biz + cleanliness_rating + 
                              guest_satisfaction_overall + bedrooms + attr_index_norm + 
                              rest_index_norm + log(dist) + log(metro_dist) + Time_Weekend + 
                              City_Athens + City_Barcelona + City_Berlin + City_Budapest + 
                              City_Lisbon + City_London + City_Paris + City_Rome + 
                              City_Vienna, 
                   data = BnB_data, coords = coordinates, verbose = TRUE, 
        longlat=TRUE, show.error.messages = TRUE)
```
After many hours, I got through 16 different bandwidth values before the CV 
scores stopped decreasing substantially. 220.4048 seems to be about as good as 
it's going to get. 




```{r geography-weighted-regression}
geo_wtd_reg <- gwr(formula = log(realSum) ~ room_shared_TRUE + person_capacity + 
                              host_is_superhost_TRUE + multi + biz + cleanliness_rating + 
                              guest_satisfaction_overall + bedrooms + attr_index_norm + 
                              rest_index_norm + log(dist) + log(metro_dist) + Time_Weekend + 
                              City_Athens + City_Barcelona + City_Berlin + City_Budapest + 
                              City_Lisbon + City_London + City_Paris + City_Rome + 
                              City_Vienna, 
                   data = BnB_data, coords = coordinates, bandwidth = 220.4048,
                   gweight = gwr.Gauss, longlat = TRUE)

head(geo_wtd_reg$SDF)

```


Now, we want to represent this data in an easier-to-read format. 

```{r gwr-results-table-and-graph}
conf_int <- function(mylist) { quantile(mylist, probs = c(0.05, 0.5, 0.95))}

gwr_intervals <- apply(X = data.frame(geo_wtd_reg$SDF), MARGIN = 2, FUN = conf_int) %>% 
  data.frame() %>% 
  select(room_shared_TRUE, person_capacity, host_is_superhost_TRUE, multi, biz, 
         cleanliness_rating, guest_satisfaction_overall, bedrooms, attr_index_norm, 
         rest_index_norm, log.dist., log.metro_dist., Time_Weekend) %>% 
  t()

kable(gwr_intervals)


gwr_intervals <- gwr_intervals %>% 
  matrix(ncol = 3) %>% 
  data.frame() %>% 
  cbind(c("Shared Room", "Person Capacity", "Superhost", "Multi", "Biz", 
          "Cleanliness Rating", "Guest Satisfaction", "Bedrooms", "Attr Index",
          "Rest Index", "Distance", "Metro Distance", "Weekend"))


colnames(gwr_intervals) <- c("Lower", "Middle", "Upper", "Variable")



ggplot(data = gwr_intervals, aes(x = Variable, y = Middle)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = Lower, ymax = Upper)) + 
  scale_x_discrete(guide = guide_axis(n.dodge = 2), labels = label_wrap_gen(10)) + 
  theme_bw() +
  labs(title = "Estimates for GWR Regression Coefficients", subtitle = "90% Error Bars", y = "Estimate")


```


The following plot needs to be fixed. 

```{r, gwr-coefficient-map-Paris}

paris_coefficients <- geo_wtd_reg$SDF[32456:39143,]


 filtered <- data.frame(BnB_data) %>%
     filter(City_Paris == 1)
   gradient_max <- quantile(paris_coefficients$`log(dist)`, prob = .75) + 1.5*(quantile(paris_coefficients$`log(dist)`, prob = .75) - quantile(paris_coefficients$`log(dist)`, prob = .25))
   gradient_min <- quantile(paris_coefficients$`log(dist)`, prob = .25) - 1.5*(quantile(paris_coefficients$`log(dist)`, prob = .75) - quantile(paris_coefficients$`log(dist)`, prob = .25))
  max_lng <- max(filtered$lng)
  min_lng <- min(filtered$lng)
  max_lat <- max(filtered$lat)
  min_lat <- min(filtered$lat)
  map_lng <- (max_lng + min_lng)/2
  map_lat <- (max_lat + min_lat)/2


gwr.point1 <- ggmap(parisMap) + 
    geom_point(data = filtered,
               mapping = aes(x=lng,y=lat, color = paris_coefficients$`log(dist)`), size = .9) +
    scale_colour_gradientn(
      colours=c('red','yellow','green'), 
      limits=c(gradient_min,gradient_max), 
      oob = scales::squish) +
    scale_x_continuous(limits = c(min_lng, max_lng), expand = c(0, 0)) +
    scale_y_continuous(limits = c(min_lat, max_lat), expand = c(0, 0)) +
    labs(title = paste("Mapping of Distance Coefficient in Paris"), y = "Latitude", 
         x = "Longitude", color = "Distance Coefficient") 
  map_name <- paste("Paris_Coefficient_Map")
  assign(map_name, gwr.point1)
  

Paris_Coefficient_Map

```


```{r gwr-coefficient-map-london}

london_coefficients <- geo_wtd_reg$SDF[22463:32455,]


 filtered <- data.frame(BnB_data) %>%
     filter(City_London == 1)
   gradient_max <- quantile(london_coefficients$`log(dist)`, prob = .75) + 1.5*(quantile(london_coefficients$`log(dist)`, prob = .75) - quantile(london_coefficients$`log(dist)`, prob = .25))
   gradient_min <- quantile(london_coefficients$`log(dist)`, prob = .25) - 1.5*(quantile(london_coefficients$`log(dist)`, prob = .75) - quantile(london_coefficients$`log(dist)`, prob = .25))
  max_lng <- max(filtered$lng)
  min_lng <- min(filtered$lng)
  max_lat <- max(filtered$lat)
  min_lat <- min(filtered$lat)
  map_lng <- (max_lng + min_lng)/2
  map_lat <- (max_lat + min_lat)/2


gwr.point1 <- ggmap(londonMap) + 
    geom_point(data = filtered,
               mapping = aes(x=lng,y=lat, color = london_coefficients$`log(dist)`), size = .9) +
    scale_colour_gradientn(
      colours=c('red','yellow','green'), 
      limits=c(gradient_min,gradient_max), 
      oob = scales::squish) +
    scale_x_continuous(limits = c(min_lng, max_lng), expand = c(0, 0)) +
    scale_y_continuous(limits = c(min_lat, max_lat), expand = c(0, 0)) +
    labs(title = paste("Mapping of Distance Coefficient in London"), y = "Latitude", 
         x = "Longitude", color = "Distance Coefficient") 
  map_name <- paste("London_Coefficient_Map")
  assign(map_name, gwr.point1)
  

London_Coefficient_Map

```









